---
title: "`r params$country`- High Frequency Reporting Completeness FY21"
author: "HFRG"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output: html_document
params:
 country: "Burundi"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

#Dependencies
library(tidyverse)
library(vroom)
library(glamr)
library(glue)
library(scales)
library(gophr)
library(lubridate)
library(RColorBrewer)
library(skimr)
library(patchwork)
library(ggrepel)
library(glitr)
library(janitor)
library(extrafont)
library(ggtext)
library(gluedown)
library(knitr)

#load your s3 creds
#setwd("C:/Users/STAR/Documents/Data")
load_secrets()

#inputs
prefix <- "HFR_Tableau" #other two options for file types - HFR_Submission, Detailed
outputfolder <- "C:/Users/STAR/Documents/Data" #change to desired output folder

#identify latest file
latest_file  <- glamr::s3_objects(
  bucket = "gov-usaid",
  prefix = glue::glue("ddc/uat/processed/hfr/outgoing/{prefix}")
) %>%
  dplyr::filter(last_modified == max(last_modified)) %>%
  dplyr::pull(key)

#download file - un-comment the below code chunk if you dont have the latest file pulled down!

#glamr::s3_download(
 # bucket = "gov-usaid",
 # object = latest_file,
 # filepath = file.path(outputfolder, basename(latest_file))
#)

#read in file
df <- vroom(file.path(outputfolder, basename(latest_file)))

date <- "2021_11_15"

#red
flag_red <- brewer.pal(5, "OrRd")[5]

```


```{r, echo = FALSE}
# AGGREGATE AND MUNGE -----------------------------------------------------
#clean period name for viz later
if("hfr_pd" %in% names(df))
  df <- mutate(df, hfr_pd = paste0(fy, ".", str_pad(hfr_pd, 2, pad = "0")))

# CREATE DF FOR OU and PARTNER ANALYSIS
df_ag_ou <- df %>%
  mutate_at(c("mer_results", "val"), ~replace(., is.na(.), 0)) %>% 
  group_by(operatingunit, countryname, orgunituid,
           fy, hfr_pd, date,
           mech_code, expect_reporting,
           indicator) %>% 
  summarise_at(vars(mer_results, hfr_results = val), sum, na.rm = TRUE) %>%
  ungroup()

#COMPLETENESS
# create flags for # of sites by mech code that are reporting HFR
# remove when there is not data from DATIM and there is a value in row

df_ag_ou <- df_ag_ou %>% 
  group_by(orgunituid, mech_code) %>% 
  mutate(has_hfr_reporting = ifelse(hfr_results > 0, TRUE, FALSE),
         is_datim_site = expect_reporting == TRUE) %>% 
  ungroup() %>% 
  filter(!(has_hfr_reporting == TRUE & is_datim_site == FALSE)) %>% 
  filter_at(vars(hfr_results, mer_results), any_vars(.!=0))

#aggregate across all sites in operatingunit
df_ag_ou <- df_ag_ou %>% 
  group_by(operatingunit, indicator,hfr_pd, date) %>% 
  summarise_at(vars(has_hfr_reporting, is_datim_site), sum, na.rm = TRUE) %>% 
  ungroup()

#calculate completeness
df_comp_ou <- df_ag_ou %>% 
  mutate(completeness = case_when(is_datim_site >  0 ~ has_hfr_reporting / is_datim_site)) 

```

# At a Glance

### This purpose of this report is to provide a snapshot of your OU's HFR Reporting Completeness in FY21. 



Here's your average HFR reporting completeness by indicator across FY21.

```{r echo = FALSE, results = 'asis'}
#average reporting completeness by indicator for OU in FY21 HFR periods
df_comp_ou_table <- df_comp_ou %>%
  filter(operatingunit == params$country,
         str_detect(hfr_pd, "2021")) %>% 
  group_by(indicator) %>% 
  summarise(mean = mean(completeness)) %>% 
  mutate(mean = percent(mean)) %>% 
  pivot_wider(names_from = indicator, values_from = mean)

knitr::kable(df_comp_ou_table)
```



Here's where you stand among other OUs in FY21. This heatmap is ordered from highest reporting completeness to lowest. 
```{r, echo = FALSE, fig.asp = 0.8, fig.width = 10}
#month
month <- max(df$date) %>% lubridate::month(label = TRUE) %>% as.character()
yr <- max(df$date) %>% lubridate::year()

#order countries
lst_order_tx <- df %>%
  filter(indicator == "TX_CURR",
         date == max(date)) %>%
  count(operatingunit, wt = mer_targets, sort = TRUE) %>%
  pull(operatingunit)

#heatmap by country and indicator
df_viz_heat_ou <- df_comp_ou %>%
  filter(indicator != "HTS_TST") %>%
  dplyr::mutate(#order_tx_curr = case_when(indicator == "TX_CURR" ~ val),
    # operatingunit = fct_reorder(operatingunit, order_tx_curr, sum, na.rm = TRUE),
  #operatingunit = factor(operatingunit, lst_order_tx), #this is where cameroon drops out
    # hfr_pd = str_sub(hfr_pd, -2),
    indicator = factor(indicator, c("TX_CURR", "TX_MMD", "TX_NEW",
                                    "HTS_TST", "HTS_TST_POS",
                                    "VMMC_CIRC", "PrEP_NEW"
    )),
    completeness = ifelse(is.infinite(completeness), NA, completeness),
    comp_lab = case_when(completeness <.75 ~ completeness),
    operatingunit = as.factor(operatingunit),
    operatingunit = fct_reorder(operatingunit, completeness),
    comp_bin = case_when(is.na(completeness) ~ NA_character_,
                         completeness == 0 ~ "0%",
                         completeness <= .25 ~ "1-25%",
                         completeness <= .5 ~ "26-50%",
                         completeness <= .75 ~ "51-75%",
                         TRUE ~ "75+%"
    )) 

bold.ou <- params$country
bold.labels <- ifelse(levels(df_viz_heat_ou$operatingunit) %in% bold.ou, yes = "bold", no = "plain")

df_viz_heat_ou %>%
  #filter(operatingunit == "Burundi") %>% 
  ggplot(aes(hfr_pd, operatingunit, fill = comp_bin)) +
  geom_tile(color = "white") +
  # geom_text(aes(label = percent(completeness,1), color = completeness > .75),
  #          family = "Source Sans Pro", size = 2.5, na.rm = TRUE) +
  facet_grid(~ indicator) +
  scale_fill_brewer(palette = "OrRd", direction = -1) +
  scale_color_manual(values = c("gray10", "gray50")) +
  #scale_y_discrete(labels = c("params$country"= expression(bold(params$country)))) +
  #scale_y_discrete(labels = function(x) highlight(x, params$country)) +
  labs(x = NULL, y = NULL,
       title = "OU Reporting Completeness",
       subtitle = "FY21 mechanism x site completeness of reporting by period",
       #caption = glue("data as of HFR {month} {yr} [{date}]"
                      ) +
  si_style_nolines() +
  # coord_fixed(ratio = 1) +
  theme(legend.position = "top",
        legend.title = element_blank(),
        legend.justification = c(0, 0),
        panel.grid = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_text(face = bold.labels),
        strip.text = element_text(hjust = 0))

```

## Partner Reporting Completeness

```{r, echo = FALSE}

# CREATE DF FOR PARTNER ---------------------------------------------------------

df_ag_partner <- df %>%
  mutate_at(c("mer_results", "val"), ~replace(., is.na(.), 0)) %>% 
  group_by(operatingunit, countryname, orgunituid,
           fy, hfr_pd, date,
           mech_code, primepartner, expect_reporting,
           indicator) %>% 
  summarise_at(vars(mer_results, hfr_results = val), sum, na.rm = TRUE) %>%
  ungroup()

df_ag_partner <- df_ag_partner %>% 
  group_by(orgunituid, mech_code) %>% 
  mutate(has_hfr_reporting = ifelse(hfr_results > 0, TRUE, FALSE),
         is_datim_site = expect_reporting == TRUE) %>% 
  ungroup() %>% 
  filter(!(has_hfr_reporting == TRUE & is_datim_site == FALSE)) %>% 
  filter_at(vars(hfr_results, mer_results), any_vars(.!=0))

df_ag_partner <- df_ag_partner %>% 
  group_by(operatingunit, indicator,hfr_pd, mech_code, primepartner, date) %>% 
  summarise_at(vars(has_hfr_reporting, is_datim_site), sum, na.rm = TRUE) %>% 
  ungroup()

df_ag_partner_comp <- df_ag_partner %>% 
  mutate(completeness = case_when(is_datim_site >  0 ~ has_hfr_reporting / is_datim_site)) 

#heatmap by country and indicator
df_viz_heat_partner <- df_ag_partner_comp %>%
  filter(indicator != "HTS_TST") %>%
  dplyr::mutate(#order_tx_curr = case_when(indicator == "TX_CURR" ~ val),
    # operatingunit = fct_reorder(operatingunit, order_tx_curr, sum, na.rm = TRUE),
   # operatingunit = factor(operatingunit, lst_order_tx), #this is where cameroon drops out
    # hfr_pd = str_sub(hfr_pd, -2),
    indicator = factor(indicator, c("TX_CURR", "TX_MMD", "TX_NEW",
                                    "HTS_TST", "HTS_TST_POS",
                                    "VMMC_CIRC", "PrEP_NEW"
    )),
    completeness = ifelse(is.infinite(completeness), NA, completeness),
    comp_lab = case_when(completeness <.75 ~ completeness),
    comp_bin = case_when(is.na(completeness) ~ NA_character_,
                        completeness == 0 ~ "0%",
                        completeness <= .25 ~ "1-25%",
                        completeness <= .5 ~ "26-50%",
                        completeness <= .75 ~ "51-75%",
                        TRUE ~ "75+%"
    )) 

```

Here's a snapshot of your partner reporting completeness across indicators

```{r, echo = FALSE, fig.asp = 0.8, fig.width = 10}
# HEATMAP BY PARTNER -------------------------------

df_viz_heat_partner %>%
  filter(operatingunit == params$country,
         !is.na(comp_bin)) %>% 
  ggplot(aes(hfr_pd, fct_rev(primepartner), fill = comp_bin)) +
  geom_tile(color = "white") +
  # geom_text(aes(label = percent(completeness,1), color = completeness > .75),
  #           family = "Source Sans Pro", size = 2.5, na.rm = TRUE) +
  facet_grid(~ indicator) +
  scale_fill_brewer(palette = "OrRd", direction = -1) +
  scale_color_manual(values = c("gray10", "gray50")) +
  labs(x = NULL, y = NULL,
       title = "Partner Reporting Completeness",
       subtitle = "FY21 mechanism x site completeness of reporting by period",
       caption = glue("data as of HFR {month} {yr} [{date}]")) +
  si_style_nolines() +
  #coord_fixed(ratio = 1) +
  theme(legend.position = "top",
        legend.title = element_blank(),
        legend.justification = c(0, 0),
        panel.grid = element_blank(),
        axis.text.x =  element_blank(),
        strip.text = element_text(hjust = 0))

```

